Community-conditioned language models for linguistic variation

### 2021-12-10 paper/paper1.tex
clarify relevance of most salient pairs

Our dataset includes messages from \num{510} subreddits, 
the set of all subreddits 
with at least \num{5000} messages per month for each month
of the year 2015.
Most but not all of these communities (with about 10 exceptions) 
are mostly English-language.
Each community corpus consist of \num{42000} randomly selected messages from the year 2015.
For each community, we reserve \num{1000} messages each for development and testing,
leaving a total of \num{20.4}M messages for training.

Messages were preprocessed as follows. 
We excluded the content of block quotes, code blocks, and tables.
We removed any markup (formatting) commands from the remaining text, 
extracting only rendered text.
We tokenized the messages using the default English model for the SpaCy tokenizer 
Version 2.2.3 \citep{Honnibal2017}.

@@

A difficulty is that the social embeddings and linguistic embeddings
range over completely unrelated spaces, so one cannot use the usual
cosine similarity metric \emph{across} this boundary. One can,
however, use cosine similarity between \emph{pairs} of communities,
and verify the similarities correlated between linguistic to social
embeddings.  This gives us a way of characterizing the differences
between the two kinds of community representation. To get a more
concrete sense of what this method yields, we first survey some of the
most salient community pairs.

>>>>

Our dataset includes messages from \num{510} subreddits, 
the set of all subreddits 
with at least \num{5000} messages per month for each month
of the year 2015.
Each community corpus consist of \num{42000} randomly selected messages from the year 2015.
For each community, we reserve \num{1000} messages each for development and testing,
leaving a total of \num{20.4}M messages for training.

Most of the communities are predominantly English-language.
Using \texttt{langid.py} \citep{Lui2012}, we observe that a majority of the overall
comments are classified as English (94.6\% of the test set) and a majority 
of communities (396 of 510) have more than 95\% of their comments classified as English.\footnote{
  We performed the classification an the message level and took the language to which \texttt{langid.py}
  assigned the highest probablity, but it is worth noting that code switching is very common on social media.}
However, it would be difficult to set a principled cutoff since 12 communities have between
50 and 95\% of their comments classified as English. 
Furthermore, relying on a tool like \texttt{langid.py} may bias 
the dataset away from communities that use a non-hegemonic variety of English.
For that reason and becasue the amount of non-English data is realtively small,
we do not attempt to filter the data.

Messages were preprocessed as follows:
We excluded the content of block quotes, code blocks, and tables.
We removed any markup (formatting) commands from the remaining text, 
extracting only rendered text.
We tokenized the messages using the default English model for the SpaCy tokenizer 
Version 2.2.3 \citep{Honnibal2017}.

@@

A difficulty is that the social embeddings and linguistic embeddings
range over completely unrelated spaces, so one cannot use the usual
cosine similarity metric \emph{across} this boundary. One can,
however, use cosine similarity between \emph{pairs} of communities,
and verify the similarities correlated between linguistic to social
embeddings.  This gives us a way of characterizing the differences
between the two kinds of community representation. To get a more
concrete sense of what this method yields, we first survey some of the
most salient community pairs. We stress that this survey is not meant
as a rigorous statistical analysis, as we shall see. Rather it is
meant to give a flavor of discrepancies and similarities existing
between linguistic and social relations.
